%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv-center-nophoto}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-blue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Javier}{Rocamora García}
\position{BIE Intern Amazon{\enskip\cdotp\enskip}M.Sc. Data Science Student{\enskip\cdotp\enskip}Computer Engineer \& Business Management}
\address{Luxembourg, Luxembourg}

\mobile{(+34) 681682613}
\linkedin{javir0c}
\email{javierrocamoragarcia@gmail.com}
%\github{javir0c}
\dateofbirth{October 24th, 1997}
\homepage{javir0c.github.io/home/}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``On a relentless quest to uncover insights from the digital realm."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Vice-Rectorate for Internationalization - North America Delegation}
  {Technical University of Madrid (UPM)\\Pº Juan XXIII, 11\\28040, Madrid}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Short research stay at MIT application}
% How the letter is opened
\letteropening{To whom it may concern,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Javier Rocamora~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}
	
I hope this letter finds you well. I am writing to express my strong interest in applying for the short resarch stay opportunity within your esteemed institution. 

Allow me to introduce myself. I am a passionate and dedicated Data Science student with a diverse educational background and a broad range of experiences that have shaped my journey thus far. Hailing from a picturesque little town in the southern-east spanish province of Alicante, I have always had an adventurous spirit and a thirst for experiencing new environments. That's the reason why I didn't miss a single chance, and I eagerly sought opportunities to discover and learn from new cultures and people. This drive led me, for example, to complete an Erasmus+ program in the city of Warsaw, Poland, or undertake an internship as a software engineer in Lübeck, Germany. Currently, I am in the final stage of completing my master’s studies from both the Technical University of Madrid and the University of Trento, Italy, fulfilling my master’s final thesys by undertaking an internship for Amazon in Luxembourg.

As I stand at the threshold of completing my academic journey, I find myself eager to apply the extensive knowledge I’ve acquired throughout my education and embrace the next phase of my growth. The practical experience I am currently gaining as a Business Intelligence Engineer intern at Amazon reinforces my belief that real-world exposure is the bridge between theory and application. Therefore, before fully immersing myself in the industry field, my goal in applying for this scholarship is to have the opportunity to delve into the world of research, learn from esteemed scholars, and gain valuable insights that will shape my future endeavors.

The resources and environment at MIT will provide me with the perfect platform to further explore my research interests and make meaningful contributions, and I have no doubt that my analytical skills and creativity will turn out to be valuable assets for this purpose. Ultimately, I see this research stay at MIT as a crucial step towards achieving my long-term goal of leveraging data-driven insights to design more sustainable and inclusive environments.

Thank you for considering my application for this exciting opportunity. I am excited to bring my passion, dedication, and diverse background to contribute to the vibrant research community at MIT and I look forward to the possibility of further discussing how I can contribute to the City Science and Engineering Research project.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
